---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
library(tidyverse)
```

# twAccount

This package includes a series of functions that allow the user to extract a brand's Twitter timeline, visualize the brand identity through the imagery posted and estimate topic models for both the timeline as well as the mentions of that brand. 

The topic modeling process relies on the `BTM` package, which is designed for short texts as opposed to standard LDA, which relies on a larger corpus. The `BTM` output is then processed using several functions borrowed from the `LDAvis` package. 



## Installation

You can install the development version of twAccount from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("taylorgrant/twAccount")
remotes::install_github("taylorgrant/twAccount")
```

## Data Extracted 

The package provides an overall wrapper function `twitter_tm()` that will (1) extract a brand's Twitter timeline, (2) recent, public tweets matching a boolean search, and (3) all images that a brand has included in its publicly available tweets. 

Once the data is extracted, a model is run to estimate topic models based upon the Biterm Topic Models algorithm in the `BTM` package. Currently, the model is specified to run based on the number of topics selected by the user, rather than running through a series of topic sizes and maximizing the log-likelihood (maybe later). The topic modeling process yields estimates of where the topics lie in 2d space, as well as the top N most salient terms for each topic (N terms specified by the user).

Estimation of the 2d space relies upon the [Jensen-Shannon Divergence](https://en.wikipedia.org/wiki/Jensen%E2%80%93Shannon_divergence){target="_blank"} methodology following by scaling with PCA. This allows for easy visualization of the topics on an X,Y axis. For example, if we took the last 3,200 tweets from the [BMWUSA](https://twitter.com/BMWUSA?ref_src=twsrc%5Egoogle%7Ctwcamp%5Eserp%7Ctwgr%5Eauthor){target="_blank"} account, a version of the 2d topic model representation would look like the below. This can be presented in a static graph, or in an html rmarkdown file using the `crosstalk` package, or you can simply use the d3 visualization from `LDAvis`.  

```{r example, out.width = '80%', echo = FALSE, fig.align="center"}
x_phi <- readRDS(here::here("data", "x_phi.rds")) 
ggplot(x_phi, aes(x = x, y = y, label = id)) +
  geom_vline(xintercept = 0, color = "gray") +
  geom_hline(yintercept = 0, color = "gray") +
  geom_point(aes(size = frac), color = my_pal('bly')[2],
             alpha = .3) +
  geom_point(aes(size = frac), shape = 1,colour = "gray") +
  geom_text(size = 3, color = "black") +
  scale_size(range = c(0, 30)) +
  theme_twg(grid = FALSE) +
  theme(legend.position = "none",
        axis.text.x = element_blank(),
        axis.text.y = element_blank()) +
  annotate("text", x = 0.01, y = (1.18*max(x_phi$y)),
           label = "PC2", color = "#303030") +
  annotate("text", x = 1.05*min(x_phi$x), y = .01,
           label = "PC1", color = '#303030') +
  labs(x = NULL, y =  NULL,
       title = "Intertopic Distance Map (via multidimensional scaling)",
       caption = expression(paste(lambda, 'set to 0.6')))
```

## Using the package 

Ideally, the user would create a new project within RStudio, but this package will build out a new directory in the current working directory of the user. 

After running the `twitter_tm()` function, the new directory will follow this structure. 

```
├── BMWUSA
│   └── [RUN DATE]
│       ├── [FIRST YEAR OF TWEETS]
│       ├── [NEXT YEAR OF TWEETS]
│       ├── [ANOTHER YEAR OF TWEETS]
│       ├── {handle}_tm_timeline.rds
│       ├── {handle}_tm_mentions.rds
│       ├── {handle}_twitter_info.rds
│       └── local_cols
└── [udpipe MODEL]
```


